Status of nuclear optical potentials and future prospects

### 2019-07-03 Notes/Candidacy/Paper/candidacy_paper.tex
Minor updates to candidacy notes

Things to include:
\\
-- r-process for motivation.
\\
-- Include multiple scattering, self-consistent Green's function methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ab initio optical potentials}
\label{sec:section_3}

@@

Things to include:
\\
-- Fitting ambiguities for phenomenological potential.
\\
-- Uncertainty quantification.

>>>>

Things to include:
\\
-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
\\
-- How do optical potentials help us understand nuclear reactions?
\\
-- r-process for motivation.
\\
-- Include multiple scattering, self-consistent Green's function methods.
\\
-- Should probably have a basic formalism section before going into phenomenology.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ab initio optical potentials} % See how papers would refer to this "microscopic"
\label{sec:section_3}

@@

Things to include:
\\
-- Fitting ambiguities for phenomenological potential.
\\
-- Uncertainty quantification.
\\
-- Add this to outlook in conclusion?
